\rule{\textwidth}{4pt}\\[1em] \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm] Regularized Payoff Approximation in Discrete Space}\\[1em] \rule{\textwidth}{2pt}

### 2025-02-19 latex/article.tex
MAE metric

Table~\ref{tab:method_comparison} presents a comparative analysis of the three regularization 
methods across different regularization parameters ($\gamma$). The Mean Absolute Percentage 
Error (MAPE) is used as the primary metric for comparison, providing a scale-independent 
measure of approximation accuracy. Lower MAPE values indicate better approximation quality.

The results demonstrate that:
\begin{itemize}
    \item L2 regularization provides consistent performance across different $\gamma$ values,
    showing good stability in the approximation.
    \item L1 regularization achieves comparable accuracy while promoting sparser solutions,
    which can be advantageous for portfolio implementation.
    \item The weighted error method shows improved accuracy in regions with larger payoff
    values, as reflected in its MAPE scores, particularly for moderate regularization values.
\end{itemize}

>>>>

Table~\ref{tab:method_comparison} presents a comparative analysis of the three regularization 
methods across different regularization parameters ($\gamma$). The Mean Absolute Error (MAE) 
is used as the primary metric for comparison, providing a direct measure of approximation accuracy 
in absolute terms. Lower MAE values indicate better approximation quality.

The results demonstrate that:
\begin{itemize}
    \item L2 regularization provides consistent performance across different $\gamma$ values,
    showing good stability in the approximation.
    \item L1 regularization achieves comparable accuracy while promoting sparser solutions,
    which can be advantageous for portfolio implementation.
    \item The weighted error method shows improved accuracy in regions with larger payoff
    values, as reflected in its MAE scores, particularly for moderate regularization values.
\end{itemize}
